\documentclass[11pt]{article}

\usepackage{color, soul, tabto, enumitem, setspace, graphicx}
%\graphicspath{...}
\onehalfspacing
\usepackage[margin=.7in, voffset=.01in]{geometry}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath, amsfonts, amsthm,  amssymb} % Math packages

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead[HL]{}
\fancyhead[HC]{\ul{WORK-IN-PROGRESS}}
\fancyhead[HR]{}
\fancyfoot[FL]{}
\fancyfoot[FC]{\ul{WORK-IN-PROGRESS}}
\fancyfoot[FR]{\thepage}
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text


%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------


\title{	
	\normalfont \normalsize 
	\huge Philosophy
}

\author{Author: Myles}

\date{Last Updated: \normalsize\today}

%----------------------------------------------------------------------------------------
%	WORK SECTION
%----------------------------------------------------------------------------------------

\begin{document}

\maketitle
\section*{\ul{HOUSE RULES}}
\begin{enumerate}
	
	\item[1.] Take responsibility for yourself.
	\item[2.] Respect yourself and others.
	\item[3.] Paradox, Humor, and Change.
	\item[4.] Karma is a Bitch.
	\item[5.] We're all brothers and sisters.
	\item[6.] You're a monster.
	\item[7.] Try not to be.
	\item[8.] Listen.
	\item[9.] Let your actions speak for you.
	\item[10.] Actions are the only things that speak.
	\item[11.] Take care of your people.
	\item[12.] Walk.
	\item[13.] Run.
	\item[14.] Don't sprint.
	\item[15.] Humility is not an option.
	\item[16.] Seek the Truth.
	\item[17.] Go your own way.
	\item[18.] Don't get cocky.
	\item[19.] God Damn.
	\item[20.] Don't lie to yourself.
	\item[21.] Learn to take a joke.
	\item[22.] Shortcuts don't count.
	\item[23.] Life is suffering.
	\item[24.] Don't be sorry.
	\item[25.] Get upright.
	\item[26.] Check yourself.
	\item[27.] Same Speed.
	\item[28.] Fundamentals first.
	\item[29.] Work from the bottom up.
	\item[30.] Nut. The. Fuck. Up.
	\item[31.] Strive for Balance.
	\item[32.] Learn to Forgive.
	\item[33.] Don't forget.
	\item[34.] Pay your dues.
	\item[35.] How do you Know?
	\item[36.] You don't Know.
	\item[37.] Trust is earned.
	\item[38.] Have Fun with it.
	\item[39.] Take it seriously.
	\item[40.] Keep your lines tight.
	\item[41.] Avoid predicting the future.
	\item[42.] Keep it simple.
	\item[43.] Oy Vey.
	\item[44.] It's a Marathon.
	\item[45.] Fuck you too.
	\item[46.] Be like water.
	\item[47.] All or Nothing.
	\item[48.] Aim for Virtue.
	\item[49.] It's a narrow Path.
	\item[50.] Fail Gracefully.
	\item[51.] Safety first, always.
	\item[52.] Business takes priority.
	\item[53.] You are your own worst Enemy.
	\item[54.] Truth Hurts.
	\item[55.] It's not meant to be easy.
	\item[56.] Work hard. Play hard.
	\item[57.] Friends are Family.
	\item[58.] This is Bible-Level Shit.
	\item[59.] Say Something. (Jesus)
	\item[60.] Respect your elders.
	\item[61.] Get Right.
	\item[62.] All Get Right.
	\item[63.] Respond with Force to Force.
	\item[64.] Numbers are not the Point.
	\item[65.] I Love you, but you're a Bitch.
	\item[66.] Fuck.
	\item[67.] God Damn It.
	\item[68.] My Bad. (God)
	\item[69.] I Have The Keys. (Myles)
	\item[70.] I LOVE YOU.
	\item[71.] You don't deserve this.
	\item[72.] You're Welcome.
	\item[73.] You Got Lucky.
	\item[74.] Exactly.
	\item[75.] Good Lord.
	\item[76.] Damn.
	\item[77.] Jesus Has The Wheel.
	\item[78.] Thank Fucking God.
	\item[79.] You're another Idiot.
	\item[80.] Jesus Saves.
	\item[81.] No Words.
	\item[82.] I am way too nice.
	\item[83.] He is. (Jesus)
	\item[84.] And you Know it.
	\item[85.] You don't Know Me.
	\item[86.] It's a Work-In-Progress.
	\item[87.] WHAT DO YOU WANT?!
	\item[88.] I. Don't. Have. To. Be. Here.
	\item[89.] You are Entitled to Nothing.
	\item[90.] Life is Hard.
	\item[91.] Don't Give-Up on Yourself.
	\item[92.] Check the House Rules.
	\item[93.] Jesus Fucking Christ.
	\item[94.] Check Your Notes.
	\item[95.] The Answer's In There Somewhere.
	\item[96.] It's Been Over.
	\item[97.] Try not to embarrass yourself.
	\item[98.] What Even The Fuck?
	\item[99.] Yeah...
	\item[100.] Life Is Good.
	
\end{enumerate}

\end{document}
