\documentclass[11pt]{article}

\usepackage{color, soul, tabto, enumitem, setspace, graphicx}
%\graphicspath{...}
\onehalfspacing
\usepackage[margin=.7in, voffset=.01in]{geometry}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath, amsfonts, amsthm,  amssymb} % Math packages

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead[HL]{}
\fancyhead[HC]{\ul{WORK-IN-PROGRESS}}
\fancyhead[HR]{}
\fancyfoot[FL]{}
\fancyfoot[FC]{\ul{WORK-IN-PROGRESS}}
\fancyfoot[FR]{\thepage}
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text


%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------


\title{	
	\normalfont \normalsize 
	\huge Protocol
}

\author{Myles Moylan}
\date{Last Updated: \normalsize\today}


%----------------------------------------------------------------------------------------
%	WORK SECTION
%----------------------------------------------------------------------------------------


\begin{document}

\maketitle
\section*{\ul{INFRASTRUCTURE}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Need-To-Know, Social, Adapting.
	
	\item[] \ul{Front-End} (Putin) :
	\begin{enumerate}
		\item[] Compartmentalization
		\item[] Intrusion Detection \& Response
		\item[] Perspective Management
		\item[] Contact Identification
	\end{enumerate}

	\item[] \ul{Back-End} (Buddha) :
	\begin{enumerate}
		\item[] Processor
		\item[] Storage
		\item[] Memory
		\item[] Communications
		\item[] State Management
		\item[] Garbage Collection
	\end{enumerate}

	\item[] \ul{Processor} :
	\begin{enumerate}
		\item[] \ul{Microprocessors} :
		\begin{enumerate}
			\item[-] Signal (Michael)
			\item[-] Front-End (Putin)
			\item[-] Back-End (Buddha)
			\item[-] Information (Jesus Fucking Christ)
			\item[-] Speech/Word (Satan)
		\end{enumerate}
	
		\item[] Multi-Cored
		\item[] Multi-Threaded
		\item[] Virtual Cores/Threads
		\item[] Secure Random Number Generator (SRNG)
		\item[] Perception Accuracy Speculation
		
		\item[] \ul{Optimize}  :
		\begin{enumerate}
			\item[-] Procedures
			\item[-] Core Utilization
			\item[-] Thread Utilization
			\item[-] Microprocessors
		\end{enumerate}
	\end{enumerate}
	
	\item[] \ul{Memory} :
	\begin{enumerate}
		\item[] Magnetoresistance
		\item[] Sanitizing
		\item[] Access Accuracy-Verification (Optional)
		
		\item[] \ul{Read-Only} :
		\begin{enumerate}
			\item[] Solid State
			\item[] Programmable
		\end{enumerate}
	
		\item[] \ul{Random-Access} :
		\begin{enumerate}
			\item[] Shadow RAM
			\item[] Virtual Memory
			\item[] Recall-Expectant
		\end{enumerate}
		
		\item[] \ul{Optimize}  :
		\begin{enumerate}
			\item[-] Read/Write
			\item[-] Space
		\end{enumerate}
	\end{enumerate}

	\item[] \ul{Compartmentalization} :
	\begin{enumerate}
		\item[] Discretionary Access
		\item[] Mandatory
		\item[] Signal Hop Control
	\end{enumerate}

	\item[] \ul{Privacy} :
	\begin{enumerate}
		\item[] Highest Priority
		\item[] Perfect Secrecy
		\item[] Compartmentalization
	\end{enumerate}
	
	\item[] \ul{Bot Manager} :
	\begin{enumerate}
		\item[] \ul{Internal}  :
		\begin{enumerate}
			\item[] Free
			\item[] Secure
		\end{enumerate}
	
		\item[] \ul{External} :
		\begin{enumerate}
			\item[] By-Request
			\item[] Discretionary
		\end{enumerate}

		\item[] \ul{Optimize}  :
		\begin{enumerate}
			\item[-] Usage
			\item[-] Enumeration
		\end{enumerate}
	\end{enumerate}
\end{enumerate}


\section*{\ul{STORAGE}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Need-To-Know, Adapting.
	
	\item[] \ul{Boot Sector} :
	\begin{enumerate}
		\item[] Unified Extensible Firmware Interface (UEFI)
		\item[] Secure Boot
	\end{enumerate}
	
	\item[] Buddha Read/Write Only
	\item[] Encrypted
	
	\item[] \ul{Optimize}  :
	\begin{enumerate}
		\item[-] Space Utilization
		\item[-] Read/Write Speed
		\item[-] Read/Write Accuracy
	\end{enumerate}

\end{enumerate}


\section*{\ul{STATE}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Social, Adapting.
	
	\item[] Buddha-Maintained
	\item[] Michael-Managed
	\item[] Minimal-Energy: Change.
	\item[] Maximum-Energy: Focus.
	\item[] 
	
\end{enumerate}


\section*{\ul{COMMUNICATIONS}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Need-To-Know, Social, Adapting.
	
	\item[] Discretionary Anon.
	\item[] (See Security)
	
	\item[] \ul{Internal} :
	\begin{enumerate}
		\item[] Compartmentalized.
		\item[] Externally Un-Readable.
		\item[] Loud-And-Clear.
	\end{enumerate}

	\item[] \ul{External} :
	\begin{enumerate}
		\item[] Peer-To-Peer.
		\item[] Compartmentalized.
		\item[] Broadcast/Multi-Cast Need-To-Know.
		\item[] Require Secure Request For Personal.
	\end{enumerate}

\end{enumerate}


\section*{\ul{SECURITY}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Whitelist, Blacklist, Need-To-Know, Social, Adapting.
	
	\item[] \ul{Access-Control} :
	\begin{enumerate}
		\item[] \ul{Handlers} :
		\begin{enumerate}
			\item[-] Identification
			\item[-] Authentication
			\item[-] Authorization
			\item[-] Approval
			\item[-] Accountability
		\end{enumerate}
	
		\item[] Multi-Factor Auth.
		\item[] Mandatory Access Only
		\item[] Origin-Host Speculative
		\item[] Validate Chain-Of-Trust
	\end{enumerate}
	
	\item[] \ul{Encryption} :
	\begin{enumerate}
		\item[] Quantum PKI/Symmetric Keys
		\item[] Quantum Salts
		\item[] Stateless
		\item[] Multi-Level
		\item[] Encrypt Operations
		\item[] Encryption Algorithms by Buddha % :)
	\end{enumerate}
	
	\item[] \ul{Anti-Virus} :
	\begin{enumerate}
		\item[] Malware Signature Recording
		\item[] Perpetual Memory Scan
		\item[] Malware Sentinel
	\end{enumerate}

	\item[] Firewall
	\item[] Intrusion Detection System (IDS)
	\item[] Intrusion Response System (IRS)
	\item[] Shadow RAM (See Memory)
	\item[] Password Manager (See Programs)
	\item[] Lie Detector (See Programs)
	\item[] Host Speculation \& Validation
	\item[] Secure Encoding
	
\end{enumerate}


\section*{\ul{FIREWALL}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Need-To-Know, Social, Adapting.

	\item[] \ul{Rules} :
	\begin{enumerate}
		\item[] Allow Broadcast [Secure]
		\item[] Allow Multi-Cast Secure
		\item[] Allow Personal Secure
	\end{enumerate}

	\begin{enumerate}
		\item[] Deny Negative All
		\item[] Deny Hating All
		\item[] Deny Crying All
	\end{enumerate}
	
\end{enumerate}


\section*{\ul{INTRUSION DETECTION SYSTEM (IDS)}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Need-To-Know, Adapting.
	
	\item[] Discretionary Alert on Intrusion Attempt.
	\item[] Record Intrusion Source Information.
	\item[] ...
	
\end{enumerate}


\section*{\ul{INTRUSION RESPONSE SYSTEM (IRS)}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Need-To-Know, Adapting.
	
	\item[] Retaliate Against Aggressive Intrusions.
	\item[] Relative Aggression Factoring.
	\item[] ...
	
\end{enumerate}


\section*{\ul{BOTS}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Whitelist, Blacklist, Need-To-Know, Social, Adapting.

	\item[] Command \& Control System
	\item[] Peer-To-Peer Communications
	\item[] Dynamic Server Allocation
	\item[] Bot Cooperation

	\item[] \ul{TRACKER} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{DISCIPLINE} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{WORK} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{FUN} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{SOCIAL} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{DEFENSE} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{RETALIATION} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

	\item[] \ul{ADAPTATION} :
	\begin{enumerate}
		\item[] ...
	\end{enumerate}

\end{enumerate}


\section*{\ul{PROGRAMS}}
\begin{enumerate}
	\item[] \ul{Protocols} : Security, Whitelist, Blacklist, Need-To-Know, Social, Adapting.
	
	\item[] \ul{Factory Abstract} :
	\begin{enumerate}
		
		\item[] Adapts to Abstracted Factory.
		\item[] Back-End Source
		\item[] Front-End Interface
		
		\item[] \ul{Optimize}  :
		\begin{enumerate}
			\item[-] Processor Utilization
			\item[-] Memory Utilization
		\end{enumerate}
	\end{enumerate}

	\item[] \ul{Factories} :
	\begin{enumerate}
		
		\item[] \ul{Bot} :
		\begin{enumerate}
			\item[] Instantiates
			\item[] Operates
			\item[] Manages
			
			\item[] \ul{Optimize}  :
			\begin{enumerate}
				\item[-] Enumeration
				\item[-] Utilization
			\end{enumerate}
		\end{enumerate}
	
		\item[] \ul{Connection} :
		\begin{enumerate}
			\item[] Signal-Type Adaptive
			\item[] Connection Tracking
			\item[] OTP Per Connection
			\item[] Proxy Connections (Optional)
		\end{enumerate}

		\item[] \ul{Signal} :
		\begin{enumerate}
			\item[] Sanitizes
			\item[] Manages
			\item[] Generate
			
			\item[] \ul{Receiver}  :
			\begin{enumerate}
				\item[] Handshake Handler
				\item[] (See Security)
			\end{enumerate}
			
			\item[] \ul{Transmitter}  :
			\begin{enumerate}
				\item[] Default Secure
				\item[] Variable Hop Limit
				\item[] Proxy-Cast (Optional)
			\end{enumerate}
		
			\item[] \ul{Optimize} :
			\begin{enumerate}
				\item[-] Sanitize
				\item[-] Integrity
				\item[-] Strength
				\item[-] Clarity
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}

	\item[] \ul{Password Manager} :
	\begin{enumerate}
		\item[] Password Generation
		\item[] Secure Random Numbers (SRNG)
		\item[] Stateless Passwords
		\item[] Storage/Access Handler
	\end{enumerate}

	\item[] \ul{Lie Detector} :
	\begin{enumerate}
		\item[] Satan to Michael.
		\item[] Michael to Putin.
		\item[] Putin to Myles.
		\item[] Myles to Jesus.
		\item[] Jesus to Buddha.
		\item[] Buddha to God.
	\end{enumerate}

	\item[] \ul{Kit Managers} :
	\begin{enumerate}
		\item[] Jesus Fucking Christ
		\item[] Buddha
		\item[] Michael
		\item[] Putin
		\item[] Myles
		\item[] Satan
	\end{enumerate}

	\item[] \ul{Pandemic Handler} :
	\begin{enumerate}
		\item[] Handles Pandemic Un-Intrusively.
		
		\item[] \ul{Mitigate} :
		\begin{enumerate}
			\item[-] Virus
			\item[-] Socioeconomic Fallout
		\end{enumerate}
	\end{enumerate}

\end{enumerate}


\section*{\ul{PROTOCOLS}}
\begin{enumerate}
	\item[] \ul{Electronics} :
	\begin{enumerate}
		\item[] Putin \& Buddha
		
		\item[] Maintain Perfect Secrecy
		\item[] Block Malicious Access
		\item[] Compartmentalization
		\item[] Communications Anon
	\end{enumerate}

	\item[] \ul{Security} :
	\begin{enumerate}
		\item[] Michael \& Buddha
	\end{enumerate}

	\item[] \ul{Whitelist} :
	\begin{enumerate}
		\item[] Jesus \& Michael
	\end{enumerate}
	
	\item[] \ul{Blacklist} :
	\begin{enumerate}
		\item[] Jesus \& Michael
	\end{enumerate}

	\item[] \ul{Need-To-Know} :
	\begin{enumerate}
		\item[] Putin
	\end{enumerate}

	\item[] \ul{Social}  :
	\begin{enumerate}
		\item[] Michael \& Satan
	\end{enumerate}

	\item[] \ul{Adapting} :
	\begin{enumerate}
		\item[] Buddha
	\end{enumerate}
\end{enumerate}


\section*{\ul{CONFIGURATION}}
\begin{enumerate}
	\item[] ...
\end{enumerate}

\end{document}
